Modal Abstractions for Virtualizing Memory Addresses

### 2023-11-16 examples.tex
drop text that is now redundant with relwork

We can see that this specification neatly encapsulates reasoning about invariants on the page tables in terms of general modal assumptions.\todo{speculative
but ought to turn out this way}

\citet{kolanski08vstte,kolanski09tphols} verified a single code block with their logic which was roughly Figure \ref{fig:mapping_code} for a 2-level ARM
page table, but several critical complexities our work deals with were not addressed.
First, beyond the limitations discussed in Section \ref{sec:overly-restrictive}, Kolanski and Klein assumed that virtual addresses
for page tables at each level were given as parameters rather than verifying any conversion from physical addresses to virtual addresses (or even axiomatizing their lookup).
In contrast, our verification articulates the address space invariant from which the physical-to-virtual translation can be implemented.
Second, our proof deals with the construction of a valid virtual points-to \emph{to the PTE to update} in mapping, which Kolanski and Klein also
assumed was given.
\todo{some of this is really an argument for our verification being more thorough, rather than being about our logic}

Reasoning about the page table walk in their logic would have required 
could reason about the walk, but would need to explicitly prove that all other invariants
of the kernel, the current address space, and all other address spaces of interest were preserved by each update, because their model
only supports separation within a single address space. In our model, this follows for free from making
our separation logic directly aware of address translation and internalizing assumptions about other address spaces as further separable assertions.
Kolanski and Klein did address part of the walk information for a 2-level page table (a possible ARM configuration), but

\textsc{seL4} currently still trusts address translations; it models page tables as a data structure in regular memory, thus not capturing the possibility that even
temporarily destroying the mappings and restoring them can actually crash the OS. \textsc{CertiKOS} papers share little in the way of precise details about
their virtual memory management, but because their core technology is based on a fork of \textsc{CompCert}, whose model of memory is
a set of unordered block allocations, we can infer their proofs must also trust these translations.

>>>>

We can see that this specification neatly encapsulates reasoning about invariants on the page tables in terms of general modal assumptions.\todo{speculative
but ought to turn out this way}
This is a simple piece of code whose functionality is critical and whose correctness is highly non-trivial. No prior work engages with this problem.

% \citet{kolanski08vstte,kolanski09tphols} verified a single code block with their logic which was roughly Figure \ref{fig:mapping_code} for a 2-level ARM
% page table, but several critical complexities our work deals with were not addressed.
% First, beyond the limitations discussed in Section \ref{sec:overly-restrictive}, Kolanski and Klein assumed that virtual addresses
% for page tables at each level were given as parameters rather than verifying any conversion from physical addresses to virtual addresses (or even axiomatizing their lookup).
% In contrast, our verification articulates the address space invariant from which the physical-to-virtual translation can be implemented.
% Second, our proof deals with the construction of a valid virtual points-to \emph{to the PTE to update} in mapping, which Kolanski and Klein also
% assumed was given.
% \todo{some of this is really an argument for our verification being more thorough, rather than being about our logic}

% Reasoning about the page table walk in their logic would have required 
% could reason about the walk, but would need to explicitly prove that all other invariants
% of the kernel, the current address space, and all other address spaces of interest were preserved by each update, because their model
% only supports separation within a single address space. In our model, this follows for free from making
% our separation logic directly aware of address translation and internalizing assumptions about other address spaces as further separable assertions.
% Kolanski and Klein did address part of the walk information for a 2-level page table (a possible ARM configuration), but

% \textsc{seL4} currently still trusts address translations; it models page tables as a data structure in regular memory, thus not capturing the possibility that even
% temporarily destroying the mappings and restoring them can actually crash the OS. \textsc{CertiKOS} papers share little in the way of precise details about
% their virtual memory management, but because their core technology is based on a fork of \textsc{CompCert}, whose model of memory is
% a set of unordered block allocations, we can infer their proofs must also trust these translations.
